Exposure Consequences - Statistics and Figures

### 2018-05-18 ManuscriptMaterials.Rmd
improved figures

Now there is a trend towards significance for the interaction between training group and movement type. That is closer to what we would expect.

@@

# Figures

Here we simply generate the same figures as above, but now they are saved as SVG files.

```{r create_svgs}
plotReachAftereffects(generateSVG=TRUE)
plotLocalization(classicOnline=TRUE, generateSVG=TRUE)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE)
```

>>>>

Still no effect...

@@

```{r create_svgs, cache=FALSE, include=FALSE}
# This chunk creates SVG files but shouldn't show up in the PDF / HTML 
plotReachAftereffects(generateSVG=TRUE)
plotLocalization(classicOnline=TRUE, generateSVG=TRUE)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE)
```
